Triangulating iconicity: Coding analysis

### 2024-09-12 paper_02_main_analyses.Rmd
+publication quality plots

### Figure 6: Ratings and cumulative iconicity

@@

plot_grid(pA,pB,labels=c("A","B"),label_size=14,rel_widths = c(1.4,2))
ggsave("figures/fig6-panelAB_ratings.png",height=5,width=9,bg="white")

@@

plot_grid(pA,pB,labels=c("A","B"),label_size=14,rel_widths = c(1.4,2))
ggsave("figures/fig6-panelAB_ratings_variant1.png",height=5,width=9,bg="white")

>>>>

### Figure 5: Ratings and cumulative iconicity

@@

plot_grid(pA,pB,labels=c("A","B"),label_size=14,rel_widths = c(1.4,2))
ggsave("figures/fig5-panelAB_ratings.png",height=5,width=9,bg="white")

@@

plot_grid(pA,pB,labels=c("A","B"),label_size=14,rel_widths = c(1.4,2))
ggsave("figures/fig5-panelAB_ratings_variant1.png",height=5,width=9,bg="white")
